### 2019-02-26 manuscript/results.tex
- B&E phone conversation notes in Discussion and Methods

We found that when considered alone, ploidy and breeding system each showed significant associations with net diversification differences. 
When considered together, however, the effect of breeding system dominated the effect of ploidy, although hidden factors played an important role as well.

@@

    \end{center}
    \caption{
        Median rate estimates for all fitted models. %B: "...all fitted/considered/evaluated models."
        Units are per million years.
        Two comma-separated numbers refer to the $A$ and $B$ hidden states, and --- means the parameter was not present in the model.
    %B: perhaps include this in the table so lazies don't have to go seeking subscripts?
    Net diversification rates ($r$) are subscripted with trait state initials (Diploid, Polyploid, Incompatible, Compatible). Transition rates are $\rho$ (polyploidization), subscripted with background breeding system state; $\delta$ (diploidization); and  $q_{IC}$ (loss of self-incompatibility).
    The upper section is for models without diploidization, and the lower section is for models with diploidization.
    The supplemental figures show the corresponding distributions of parameter estimates.
    }
    \label{table:estimates}
\end{supptable}
%B: The I/C and I/C+A/B columns should be in the top panel, no (they don't have rho)? I'll do this in a separate doc first. %FIXME

>>>>

%B: how about below; was: We found that when considered alone, ploidy and breeding system each showed significant associations with net diversification differences. 
Individual trait-dependent diversification inference, of ploidy and breeding system considered separately, each showed significant associations with net diversification differences. 
When considered together, however, the effect of breeding system dominated the effect of ploidy, although hidden factors played an important role as well.

@@

    \end{center}
    \caption{
        Median rate estimates for all fitted models. %B: "...all fitted/considered/evaluated models."
        Units are per million years.
        Two comma-separated numbers refer to the $A$ and $B$ hidden states, and --- means the parameter was not present in the model.
    %B: perhaps include this in the table so lazies don't have to go seeking subscripts?
    Net diversification rates ($r$) are subscripted with trait state initials (Diploid, Polyploid, Incompatible, Compatible). Transition rates are $\rho$ (polyploidization), subscripted with background breeding system state; $\delta$ (diploidization); and  $q_{IC}$ (loss of self-incompatibility).
    The upper section is for models without diploidization, and the lower section is for models with diploidization.
    The supplemental figures show the corresponding distributions of parameter estimates.
    }
    \label{table:estimates}
\end{supptable}

%B: FIXME:
%B: Table S2 (above) The I/C and I/C+A/B columns should maybe appear in the top panel, no?
%B: I did not flip the panels, because I realized just now that we'll first discuss no-delta, then delta. Is that okay?
%
% check values of delta and rho D/P+A/B with(out) delta
% i.e. parameter values in figure S1 & S4 vs Table S2
